R Notebook

### 2018-11-13 main_latemar.Rmd
updated functions path

loading the functions, replace with the location of your files
```{r}
source("C:/Users/tl3315/Desktop/GitHub/CyclicPGS/co_sim_condi.R")
source("C:/Users/tl3315/Desktop/GitHub/CyclicPGS/cosim_functions.R")
```
Two libraries used that you first need to install with R

>>>>

loading the functions, replace with the location of your files
```{r}
source("co_sim_condi.R")
source("cosim_functions.R")
```
Two libraries used that you first need to install with R
